%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents

First of all, I want to thank my supervisors, Professor David Cahen and Doctor Hugo Meekes.\\
Professor David Cahen accepted me into his research group and thus enabled me to experience one of the most interesting and valuable years of my life, both in terms of personal experience and academic development. He was kind enough to give me a chance to round off my project even after I had stayed out of contact for more than a year.\\
My thanks to Doctor Hugo Meekes is especially due to the fact that he more or less spontaneously, on the spot, decided that he would be my Examiner, being willing to put in a lot of work for a student whom he didn't really know and who is not otherwise connected to his department or research.\\
Every member of the Optoelectronic Materials Group has my thanks but I want to point out especially Igal Levine who supported me, pushed me on and helped me remain focused on the \McA{}, Nir Kedem who was always willing to listen to the woes of a Masters Student, helped out with deep experimental insight and gave the sparkling idea to try vanadium oxide as a model system, to Ann Erickson who is not a member of the Group any more, but brought me on the way of my project and whose understanding of the Physics of Solar Cells was a valuable source of information. Tal Toledano helped me with the \ftir{} and remained calm even when I messed up his complicated synthesis set ups, Dr. Lee Barnea introduced me into the finer points of \cpd{} and \spv{}, Arava Zohar helped greatly with silicon preparations and \enhyphen{general} experimentation. Dr. Sabyasachi \enhyphen{Sachi} Mukhopadhyay helped me remain positive whenever doubt hit and Dr. Lior Sepunaro not only introduced me to fundamental techniques, but was there to listen to and share personal experiences in our many brakes. He also makes the most excellent espresso.\\
I also want to include my parents, all three of them, Suzan Emre, Stephan Bretten and Kornelia Hewel in this acknowledgement. I had given up and only through their unconditional support did I ever try to finish what I started.\\
\textbf{Thank you all.}

\end{acknowledgements}
